### 2019-08-21 maciek.tex
Omega(kl)

>>>>

  \begin{enumerate}
    \item Clusters A and B with components of size k-1. Define x and y.
    \item The input sequence (after these glueing) is to keep asking for x and someone of x's color
    \item Define a sequence of xs and ys for any deterministic algorithm.
    \item Define what OPT should do: the cluster D and nodes d1 d2 that should be hidden from the sequence of xs (and ys?)
    \item (somewhere) define c(x): it is easy when x is not from D: then any would do; if x is from D, then issue request between non-d1/d2
    \item Argue that OPT does not pay for input sequence (after glueing)
    \item bound the number of times we can issue (x, c(x)) request
  \end{enumerate}
\end{proof}
